---
title: "Multiple Regression Model"
author: "Thach Pham"
date: "15/11/2018"
output: pdf_document
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The experiment uses @R-base and some packages developed by @R-ggplot2, @R-rmarkdown, @R-GGally, @R-lmtest, @R-car, @R-stargazer, @R-tidyverse, and @R-wooldridge.
```{r, message=F, warning=F}
library(wooldridge)
library(stargazer)
library(car)
library(lmtest)
library(tidyverse)
library(GGally) 
# For ggiraphExtra require: devtools, libcairo2-dev and libudunits2-dev
# devtools::install_github("cardiomoon/ggiraphExtra")
# library(ggiraph)
# library(ggiraphExtra)
```

# Descriptive Statistics of wage1 data
```{r, message=F, warning=F}
data(wage1)
desc.wage1 <- select(wage1, c(wage, educ, exper, tenure, lwage))
stargazer(desc.wage1, type = "text", style = "qje", title = "Descriptive Statistics",
          digits = 4, out = "MRO/Descriptive Statistics.doc")
```

# Distribution of Wage
```{r, message=F, warning=F}
(wage.dist <- ggplot(desc.wage1, aes(wage)) + 
  geom_histogram(aes(y = ..density..), bindwidth = 0.5, colour = "blue", fill = "white") +
  geom_density(alpha = 0.2, fill = "#FF6666") +
  labs(x = "Wage", y = "Density", title = "Wage Distribution") +
  geom_vline(aes(xintercept = mean(wage)), color = "red", linetype = "dashed", size = 1) +
  geom_vline(aes(xintercept = median(wage)), color = "blue", linetype ="dashed", size = 1))
ggsave("MRO/Wage Distribution.png", wage.dist)
```

# Distribution of Log Wage
```{r, message=F, warning=F}
(lwage.dist <- ggplot(desc.wage1, aes(lwage)) + 
  geom_histogram(aes(y = ..density..), bindwidth = 0.5, colour = "blue", fill = "white") +
  geom_density(alpha = 0.2, fill = "#FF6666") +
  labs(x = "Log Wage", y = "Density", title = "Log Wage Distribution") +
  geom_vline(aes(xintercept = mean(lwage)), color = "red", linetype = "dashed", size = 1) +
  geom_vline(aes(xintercept = median(lwage)), color = "blue", linetype ="dashed", size = 1))
ggsave("MRO/Log Wage Distribution.png", lwage.dist)
```

# Distribution of Education
```{r, message=F, warning=F}
(educ.dist <- ggplot(desc.wage1, aes(educ)) + 
  geom_histogram(aes(y = ..density..), bindwidth = 0.5, colour = "blue", fill = "white") +
  geom_density(alpha = 0.2, fill = "#FF6666") +
  labs(x = "Education", y = "Density", title = "Education Distribution") +
  geom_vline(aes(xintercept = mean(educ)), color = "red", linetype = "dashed", size = 1) +
  geom_vline(aes(xintercept = median(educ)), color = "blue", linetype ="dashed", size = 1))
ggsave("MRO/Education Distribution.png", educ.dist)
```

# Distribution of Experience
```{r, message=F, warning=F}
(exper.dist <- ggplot(desc.wage1, aes(exper)) + 
  geom_histogram(aes(y = ..density..), bindwidth = 0.5, colour = "blue", fill = "white") +
  geom_density(alpha = 0.2, fill = "#FF6666") +
  labs(x = "Experience", y = "Density", title = "Experience Distribution") +
  geom_vline(aes(xintercept = mean(exper)), color = "red", linetype = "dashed", size = 1) +
  geom_vline(aes(xintercept = median(exper)), color = "blue", linetype ="dashed", size = 1))
ggsave("MRO/Experience Distribution.png", exper.dist)
```

# Distribution of Tenure
```{r}
(tenure.dist <- ggplot(desc.wage1, aes(tenure)) + 
  geom_histogram(aes(y = ..density..), bindwidth = 0.5, colour = "blue", fill = "white") +
  geom_density(alpha = 0.2, fill = "#FF6666") +
  labs(x = "Tenure", y = "Density", title = "Tenure Distribution") +
  geom_vline(aes(xintercept = mean(tenure)), color = "red", linetype = "dashed", size = 1) +
  geom_vline(aes(xintercept = median(tenure)), color = "blue", linetype ="dashed", size = 1))
ggsave("MRO/Tenure Distribution.png", tenure.dist)
```

# Covariance and Correlation Matrix
```{r}
cov(desc.wage1)
```

# Correlation Matrix
```{r, message=F, warning=F}
cor.graph <- ggpairs(desc.wage1, title = "Correlation Matrix")
ggsave("MRO/Correltaion Matrix.png", cor.graph)
```

# Model 1
```{r, message=F, warning=F}
model1 <- lm(wage ~ educ + exper + tenure, data = desc.wage1)
stargazer(model1, type = "text", title = "lm(wage ~ educ + exper + tenure)", 
          style = "qje", out = "MRO/model1.doc")
#ggPredict(model1, se = T, interactive = T)
```

# Multicollinearity of Model 1
```{r}
vif(model1)
```

# Checking Normal Distribution of Error Term (Model 1)
```{r}
shapiro.test(residuals(model1))
(error.model1 <- ggplot(model1, aes(sample = model1$residuals)) +
  stat_qq(col = "blue") +
  stat_qq_line(col = "red", lty = 2) +
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles", title = "QQ Plot ERR1"))
ggsave("MRO/QQ Plot ERR1.png", error.model1)
```

# Test of Heteroskedasticity of Model 1
```{r}
bptest(model1)
```

# Robust coefficients using White's robust SE (Model1 )
```{r}
coeftest(model1, vcov = hccm(model1, type = "hc0"))
```

# Model 2
```{r}
model2 <- lm(lwage ~ educ + exper + tenure, data = desc.wage1)
stargazer(model2, type = "text", title = "lm(lwage ~ educ + exper + tenure)", 
          style = "qje", out = "MRO/model2.doc")
#ggPredict(model2, se = T, interactive = T)
```

# Multicollinearity of Model 2
```{r}
vif(model2)
```

# Checking Normal Distribution of Error Term (Model 2)
```{r}
shapiro.test(residuals(model2))
(error.model2 <- ggplot(model2, aes(sample = model2$residuals)) +
  stat_qq(col = "blue") +
  stat_qq_line(col = "red", lty = 2) +
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles", title = "QQ Plot ERR2"))
ggsave("MRO/QQ Plot ERR2.png", error.model2)
```

# Test of Heteroskedasticity of Model 2
```{r}
bptest(model2)
```

# Robust coefficients using White's robust SE (Model 2)
```{r}
coeftest(model2, vcov = hccm(model2, type = "hc0"))
```

# References